\documentclass[a4paper, 11pt]{article}

\usepackage{colortbl}

\usepackage{bm}
\usepackage{CV}
%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{xcolor}
\usepackage{color}
\usepackage{fourier}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}

\usepackage[T1]{fontenc}
\usepackage{titlecaps}
\usepackage[bitstream-charter]{mathdesign}
\usepackage[latin1]{inputenc}                           % Input encoding

\usepackage{paralist}

\setlength{\parskip}{8pt}
\renewcommand{\baselinestretch}{1.12}
%\addtolength{\textwidth}{1.2in} \addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\textheight}{0.9in} \addtolength{\topmargin}{-0.62in}
\addtolength{\textwidth}{1in} \addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textheight}{1in} \addtolength{\topmargin}{-0.62in}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\begin{document}\large
\parindent 0em
\thispagestyle{myheadings}

\cvname{Ning gao} \cvaddress{Data Scientist @ Microsoft}{http://ninggao.github.io} \cvemail{E-mail: nigao@microsoft.com} \makecvtitle


%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\begin{CV}
\item[2012--2018] University of Maryland, College Park\\
Advisor: Dr. Douglas W. Oard\\
\textbf{Ph.D. Candidate in Information Studies}\\
Thesis: Towards Knowledge Base Population from Conversational Sources
\vspace{2mm}

\item[2009--2012] Peking University\\
 Advisor: Dr. Zhi-hong Deng\\
\textbf{M.S. in Electronic Engineering and Computer Science}
\vspace{2mm}

\item[2005--2009] Peking University

\textbf{B.S. in Electronic Engineering and Computer Science}
\end{CV}
\vspace{-1mm}



%\section{Research Experience}



%\vspace{3mm}

%\section{Grants}

%Helped Dr. Han Liu in the preparation of grant titled ``Large-Scale Semiparametric Graphical Models with Applications to Neuroscience", Sponsored by the Research Project Grant Program (R01) at National Institute of Health (NIH) in 2013. 

\vspace{-1mm}
\section{Peer-reviewed Conference Papers}

\begin{itemize}

\item[\color{bl3} 1.]{\scshape\color{bl3}\bf Entity Linking to One Thousand Knowledge Bases}\\
{\color{black} \textbf{Ning Gao}, and Silviu Cucerzan \\
\emph{Proceedings of the 39th European Conference on Information Retrieval (ECIR 2017).\\ Acceptance rate 27\%}}
\vspace{2mm}

\item[\color{bl3} 2.]{\scshape\color{bl3}\bf Reducing Reliance on Relevance Judgments for System Comparison by Using Expectation-Maximization}\\
\color{black}{\textbf{Ning Gao}}, William Webber, and Douglas W. Oard\\
\emph{Proceedings of the of the 36th European Conference on Information Retrieval (ECIR 2014): pp. 1-12.\\ Acceptance rate 23\%.}
\vspace{2mm}

\item[\color{bl3} 3.]{\scshape\color{bl3}\bf Leveraging Side Information for Speaker Identification with the Enron Conversational Telephone Speech Collection}\\
\color{black}{\textbf{Ning Gao}}, Gregory Sell, Douglas W. Oard, and Mark Dredze\\
\emph{IEEE Automatic Speech Recognition and Understanding Workshop  (ASRU 2017).\\ Acceptance rate 45\%.}
\vspace{2mm}


\item[\color{bl3} 4.]{\scshape\color{bl3}\bf Support for Interactive Identification of Mentioned Entities in Conversational Speech}\\
{\color{black} \textbf{Ning Gao}, Douglas W. Oard, and Mark Dredze \\
\emph{Proceedings of the 40th International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR 2017).\\ Acceptance rate 30\%.}}
\vspace{2mm}

\item[\color{bl3} 5.]{\scshape\color{bl3}\bf Pearson Rank: A Head-Weighted Gap-Sensitive Score-Based Correlation Coefficient}\\
{\color{black} \textbf{Ning Gao}, Mossaab Bagdouri, and Douglas W. Oard \\
\emph{Proceedings of the 39th International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR 2016): pp. 941-944.\\ Acceptance rate 31\%.}}
\vspace{2mm}



\item[\color{bl3} 6.]{\scshape\color{bl3}\bf A Head-Weighted Gap-Sensitive Correlation Coefficient}\\
{\color{black} \textbf{Ning Gao}, and Douglas W. Oard} \\
\emph{Proceedings of the 38th international ACM SIGIR conference on Research \& development in information retrieval (SIGIR 2015): pp. 799-802.\\ Acceptance rate 31\%.}
\vspace{2mm}

\item[\color{bl3} 7.]{\scshape\color{bl3}\bf Enhancing Scientific Collaboration Through Knowledge Base Population and Linking for Meetings}\\
\color{black}{\textbf{Ning Gao}}, Mark Dredze, and Douglas Oard\\
\emph{Hawaii International Conference on System Sciences (HICSS 2017).}
\vspace{2mm}

\item[\color{bl3} 8.]{\scshape\color{bl3}\bf Knowledge Base Population for Organization Mentions in Email}\\
{\color{black} \textbf{Ning Gao}, Mark Dredze, and Douglas W. Oard \\
\emph{5th Workshop on Automated Knowledge Base Construction (AKBC 2016), 5 pages.}}
\vspace{2mm}

\item[\color{bl3} 9.]{\scshape\color{bl3}\bf HLTCOE participation in TAC KBP 2015: Cold start and TEDL}\\
{\color{black}Tim Finin, Dawn Lawrie, Paul McNamee, James Mayfield, Douglas Oard, Nanyun Peng, \textbf{Ning Gao}, Yiu-Chang Lin, Josh MacLin, and Tim Dowd \\
\emph{Proceedings of the Eighth Text Analysis Conference (TAC 2015), 14 pages.}}
\vspace{2mm}




\item[\color{bl3} 10.]{\scshape\color{bl3}\bf A Test Collection for Email Entity Linking}\\
{\color{black} \textbf{Ning Gao}, Douglas W. Oard, and Mark Dredze \\
\emph{NIPS Workshop on Automated Knowledge Base Construction (AKBC 2014), 5 pages.}}
\vspace{2mm}

        
\item[\color{bl3} 11.]{\scshape\color{bl3}\bf Guess What I Want: Inferring the Semantics of Keyword Queries Using Evidence Theory}\\
\color{black}{Jia-Jian Jiang, Zhi-Hong Deng, \textbf{Ning Gao}, and Sheng-Long Lv}\\
\emph{ Asia-Pacific Web Conference (APWeb 2012): pp. 388-398.}
\vspace{2mm}



\item[\color{bl3} 12.]{\scshape\color{bl3}\bf Report on the SIGIR Workshop on ``Entertain Me": supporting complex search tasks}\\
\color{black}{Nicholas J. Belkin, Charles L. A. Clarke, \textbf{Ning Gao}, Jaap Kamps, and Jussi Karlgren}\\
\emph{ ACM SIGIR Forum (2011): pp. 51-59.}
\vspace{2mm}

\item[\color{bl3} 13.]{\scshape\color{bl3}\bf Fully Utilize Feedbacks: Language Model Based Relevance Feedback in Information Retrieval}\\
\color{black}{Sheng-Long Lv, Zhi-Hong Deng, Hang Yu, \textbf{Ning Gao}, and Jia-Jian Jiang}\\
\emph{ Advanced Data Mining and Applications (ADMA 2011): pp. 395-405.}
\vspace{2mm}

\item[\color{bl3} 14.]{\scshape\color{bl3}\bf ListOPT: Learning to Optimize for XML Ranking}\\
\color{black}{\textbf{Ning Gao}, Zhi-Hong Deng, Hang Yu, and Jia-Jian Jiang}\\
\emph{ Pacific-Asia Conference on Knowledge Discovery and Data Mining (PAKDD 2011): pp. 482-492.\\Acceptance Rate 27\%.}

\vspace{2mm}

\item[\color{bl3} 15.]{\scshape\color{bl3}\bf Adaptive Top-k Algorithm in SLCA-Based XML Keyword Search}\\
\color{black}{Hang Yu, Zhi-Hong Deng, Yong-Qing Xiang, and \textbf{Ning Gao}}\\
\emph{ Asia-Pacific Web Conference (APWeb 2010): pp. 364-366.}
\vspace{2mm}

\item[\color{bl3} 16.]{\scshape\color{bl3}\bf A New Indexing Strategy for XML Keyword Search}\\
\color{black}{Yong-Qing Xiang, Zhi-Hong Deng, Hang Yu, Sijing Wang, and \textbf{Ning Gao}}\\
\emph{ Seventh International Conference on Fuzzy Systems and Knowledge Discovery (FSKD 2010): pp. 2412-2416.}
\vspace{2mm}

\item[\color{bl3} 17.]{\scshape\color{bl3}\bf Combining Strategies for XML Retrieval}\\
\color{black}{\textbf{Ning Gao}, Zhi-Hong Deng, Jia-Jian Jiang, Sheng-Long Lv, and Hang Yu}\\
\emph{ Initiative for the Evaluation of XML Retrieval (INEX 2010): pp. 319-331.}\\
\color{red}{\bf (INEX 2010 Best Student Paper Award)}
\vspace{2mm}


\item[\color{bl3} 18.]{\scshape\color{bl3}\bf A Learning-to-Rank Method for XML Keyword Search}\\
\color{black}{\textbf{Ning Gao}, Zhi-Hong Deng, Yong-Qing Xiang, and Hang Yu}\\
\emph{ Initiative for the Evaluation of XML Retrieval (INEX 2009): pp. 81-87.}

 \end{itemize}        

\section{Peer-reviewed Journal Papers}
\begin{itemize}

\item[\color{bl3} 19.]{\scshape\color{bl3}\bf Person Entity Linking in Email with NIL Detection}\\
\color{black}{\textbf{Ning Gao}}, Mark Dredze, and Douglas W. Oard\\
\emph{Journal of the Association for Information Science and Technology (2017).}
\vspace{2mm}

\item[\color{bl3} 20.]{\scshape\color{bl3}\bf XDist: An Effective XML Keyword Search System With Re-ranking Model Based on Keyword Distribution}\\
\color{black}{\textbf{Ning Gao}}, ZhiHong Deng, and ShengLong Lv\\
\emph{Science China Information Sciences 57.5 (2014): pp. 1-17.}
\vspace{2mm}

\item[\color{bl3} 21.]{\scshape\color{bl3}\bf  LAF: A New XML Encoding and Indexing Strategy for Keyword-based XML Search}\\
\color{black}{Zhi-Hong Deng, Yong-Qing Xiang, and \textbf{Ning Gao}}\\
\emph{ Concurrency and Computation: Practice and Experience 25(11) (2013): pp. 1604-1621.}
\vspace{2mm}

\item[\color{bl3} 22.]{\scshape\color{bl3}\bf  Efficient Top-k Algorithm for eXtensible Markup Language Keyword Search}\\
\color{black}{Hang Yu, Zhi-Hong Deng, and \textbf{Ning Gao}}\\
\emph{IET Software 6(4) (2012): pp. 342-349.}
\vspace{2mm}

\item[\color{bl3} 23.]{\scshape\color{bl3}\bf MAXLCA: A New Query Semantic Model for XML Keyword Search}\\
\color{black}{\textbf{Ning Gao}, Zhi-Hong Deng, Jia-Jian Jiang, and Hang Yu}\\
\emph{Journal of Web Engineering 11(2) (2012): pp. 131-145.}
\vspace{2mm}

\item[\color{bl3} 24.]{\scshape\color{bl3}\bf Mop: An Efficient Algorithm for Mining Frequent Pattern with Subtree Traversing}\\
\color{black}{Zhi-Hong Deng, \textbf{Ning Gao}, and Xiaoran Xu}\\
\emph{ Fundamenta Informaticae. 111(4)(2011): pp. 373-390.}
\vspace{2mm}


\end{itemize}

%\section{Work in Progress}
%\begin{itemize}


%\item[\color{bl3} 22.]{\scshape\color{bl3}\bf Entity Searching for Conversational Telephone Speech}\\
%\color{black}{\textbf{Ning Gao}}, Douglas Oard, and Mark Dredze\\
%\emph{Under review for 40th International ACM SIGIR Conference on Research and Development in Information Retrieval, 2017.}
%\vspace{2mm}

%\item[\color{bl3} 23.]{\scshape\color{bl3}\bf Enhancing Speaker Recognition with Text-Based Techniques}\\
%\color{black}{\textbf{Ning Gao}}, Greg Sell, Mark Dredze, and Douglas Oard\\
%\emph{In preparation for Interspeech 2017.}
%\vspace{2mm}

%\item[\color{bl3} 24.]{\scshape\color{bl3}\bf Active Named Entity Recognition for Domain-Specific Collections}\\
%\color{black}{\textbf{Ning Gao}}, Nikos Karampatziakis, and Rahul Potharaju\\
%\emph{In preparation for the 55th annual meeting of the Association for Computational Linguistics (ACL) 2017.}
%\vspace{2mm}

%\end{itemize}

\section{Awards and Scholarships}
\begin{CV}
\item [2016 $\sim$ 2017] {\red{\textbf{iFellows Doctoral Fellowship}} \\ The Andrew W. Mellon Foundation.}\vspace{2mm}

\item[2015]{\textbf{SIGIR Travel Grant}\\ 38th international ACM SIGIR conference on Research \& development in information retrieval.}
\vspace{2mm}

\item[2014]{\textbf{Jacob K. Goldhaber Travel Grant}\\ Office of the President and the Graduate School, University of Maryland.}
\vspace{2mm}

\item[2014]{\textbf{International Conference Student Support Award}\\ Office of the President and the Graduate School, University of Maryland.}
\vspace{2mm}

        \item[2012]{\textbf{Best Poster Award Runner-up}\\ iSchool Doctoral Research Day, Information Studies, University of Maryland.}
        \vspace{2mm}

        \item[2011]{\red{\textbf{Founder Scholarship}}\\ Peking University Founder Group Co.,Ltd (For best student in AI)}
        \vspace{2mm}

        \item[2010]{\red{\textbf{Best Student Paper Award}}\\ Workshop of INitiative for the Evaluation of XML Retrieval (INEX)}
        \vspace{2mm}

        \item[2009 $\sim$ 2012]{\textbf{College Scholarship}\\ School of Electronic Engineering and Computer Science, Peking University}

\end{CV}



\section{Professional Membership}
\begin{itemize}
\item
Program Committee Member of \textbf{iConference 2016}
\vspace{2mm}
\item
Program Committee Member of \textbf{iConference 2015}
\vspace{2mm}
\item
Co-organizer of \textbf{SIGIR 2011 Workshop on ``Entertain Me"}\\
\emph{Other Co-organizers: 
\begin{itemize}
\item Nick Belkin, Rutgers, USA
\item Charlie Clarke, Waterloo, Canada
\item Jaap Kamps, University of Amsterdam, The Netherlands
\item Jussi Karlgren, SICS Stockholm, Sweden
\end{itemize}
}
\vspace{2mm}
\item
Program Committee Member of  \textbf{Initiative for the Evaluation of XML retrieval (INEX) 2010}
\end{itemize}


%\section{Teaching Experience}
%\begin{CV}
%\item [2011 Spring] {Teaching Assistant of \textbf{Introduction to Machine Learning}, for B.Sc. students}\\Primary Instructor: Zhihong Deng, Peking University
%\vspace{2mm}
%\item [2011 Fall] {Teaching Assistant of \textbf{Web Data Warehouses}, for M.Sc. students.}\\Primary Instructor: Zhihong Deng, Peking University
%\vspace{2mm}
%\item [2012 Spring] {Teaching Assistant of \textbf{Intelligent Information Retrieval and Web Search}, for M.Sc. students.}\\Primary Instructor: Zhihong Deng, Peking University



%\end{CV}

\section{Internship}
\begin{CV}
\item[2015 May $\sim$ Aug]Microsoft Cloud and Information Service Lab, Redmond\\
Advisor: Nikos Karampatziakis\\
\item[2014 Jun $\sim$ Aug]Microsoft Research, Redmond\\
Advisor: Silviu-Petru Cucerzan
\end{CV}

\section{Skills}
\begin{itemize}

\item \textbf{Language}: English (Fluent), Chinese-Mandarin (Native)
\end{itemize}
    








\end{document}
